---
title: "Project 4 - Main Script"
author: "Xuehan Liu, Hongyi Zhu, Mengchen Li"
date: "04/05/2017"
output: pdf_document
---

This file is to combine two paper together and compare the algorithm performance

############################ Paper3: Naive Bayes Algorithm ######################################

This file is an attempt to the Naive Bayes algorithm from "Two Supervised Learning Approaches for Name Disambiguation in Author Citations" Han(2004). 

## Step 0: Load the packages, specify directories

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)

if (!require("splitstackshape")) install.packages("splitstackshape")
library(splitstackshape)


if (!require("matrixStats")) install.packages("matrixStats")
library(matrixStats)

if (!require("reshape2")) install.packages("reshape2")
library(reshape2)
```

## Step 1: Load and process the data

Please run "data cleaner.Rmd" first so that the .txt files are all in .csv format for processing.

```{r}
dat = read.csv("../data/nameset/A Kumar.csv")
test = data.frame()
train = data.frame()

# sample the dataset by author ID
for (i in 1:max(dat$author.ID))
{
  sub = subset(dat, author.ID == i)
  sam_index = sample(nrow(sub), floor(nrow(sub)/2))
  sam = sub[sam_index, ]
  train = rbind(train, sam)
  antisam = sub[-sam_index ,]
  test = rbind(test, antisam)
}
rm(sub, sam, i, sam_index, antisam)

```

## Step 2: Setting up variable names for Naive Bayes

These are placeholder variables used for the subsequent calculations.

```{r}

  # number vectors
  
  # calculate the number of authors in the dataset
  numauthor = max(train$author.ID)
  # to count the number of paper for each author
  numpaper = rep(0, numauthor)
  # to count the number of paper authored with coauthors
  numpapercoauthor = rep(0, numauthor)
  # number of paper the author writes alone
  numpapernocoauthor = rep(0, numauthor)
  # number of coauthors each author has
  numcoauthor = rep("", numauthor)
  
  
  
  # probability vectors
  
  # initialize P(xi), prior probabilities vector
  p_xi = rep(0, numauthor)
  # P(seen|Co, Xi)
  p_seen.co = rep(0, numauthor)
  # initialize P(A1k|xi), likelihood vector
  p_A1k.X = data.frame()
  # P(A1k|co, seen, Xi)
  p_A1k.seen = data.frame()
  # P(A1K|co, unseen, Xi)
  p_A1k.unseen = data.frame()
  # P(A1|X)
  p_A1.X = data.frame()
  
```
  
  
## Step 3: Calculate the likelihood of seeing feature one, coauthors.
These values are the log of conditional probabilities of author Xi collaborating with each and every one of the coauthors.
  
```{r}
  
  # calculate number of paper each author.ID writes
  for (i in 1:numauthor)
  {
    numpaper[i] = sum(train$author.ID==i)
  }
  
  # number of coauthor an author has
  numpapercoauthor = numpaper - numpapernocoauthor
  
  
  # find the number of paper author writes alone
  for (i in 1:numauthor)
  {
    numpapernocoauthor[i] = sum(train$coauthor.names==""&train$author.ID==i)
  }
  
  
  # extract all coauthors and put them into a list
  coauthor.count = data.frame(cbind(train$author.ID, as.character(train$coauthor.names)))
  
  colnames (coauthor.count) = c("author.ID", "coauthor.names")
  
  coauthor.count = cSplit(coauthor.count, "coauthor.names", ",", "long")[
    , list(collaboaration.times = .N), .(author.ID, coauthor.names)][]
  
  
  # create a complete coauthor matrix
  coauthor.matrix = dcast(coauthor.count, author.ID~...)
  if("NA" %in% colnames(coauthor.matrix))
  {
    coauthor.matrix$`NA`=NULL
  }
  
  
  coauthor.matrix[is.na(coauthor.matrix)]=0
  
  
  # calculate P(seen|Co, xi) and store in coauthor.matrix$seen
  for (i in 1: numauthor)
  {
    p_seen.co[i] = sum(as.numeric(coauthor.matrix[i,-1])>1) / sum(as.numeric(coauthor.matrix[i,-1])>0)
  }
  
  
  # filter only coauthors with collaboration times >1
  seen <- coauthor.count[coauthor.count$collaboaration.times!=1,]
  # convert this count list to a dataframe
  coauthor.seen.matrix <- dcast(seen, author.ID~...) 
  # change NAs to zero
  coauthor.seen.matrix[is.na(coauthor.seen.matrix)]<- 0
  if("NA" %in% colnames(coauthor.seen.matrix))
  {
    coauthor.seen.matrix$`NA`=NULL
  }
  
  # do the same for unseen coauthors:
  # unseen coauthors
  unseen = coauthor.count[coauthor.count$collaboaration.times==1, ]
  # convert list to df
  coauthor.unseen.matrix <- dcast(unseen, author.ID~...) 
  # change NAs to zero
  coauthor.unseen.matrix[is.na(coauthor.unseen.matrix)]<- 0
  if("NA" %in% colnames(coauthor.unseen.matrix))
  {
    coauthor.unseen.matrix$`NA`=NULL
  }
  
  
  # calculate P(xi)
  p_xi = table(train$author.ID)/sum(table(train$author.ID))
  
  # P(N|xi), probability of writing next paper alone
  p_numpapernocoauthor = numpapernocoauthor/numpaper
  
  
  # generate an empty matrix with same dim with coauthor.seen.matrix
  p_A1k.seen <- data.frame(matrix(rep(0,ncol(coauthor.seen.matrix)*numauthor),nrow = numauthor))
  
  ID <- coauthor.matrix$author.ID
  p_A1k.seen <- data.frame(ID, p_A1k.seen)
  colnames(p_A1k.seen) <- colnames(coauthor.seen.matrix)
  row.names(p_A1k.seen) <- coauthor.matrix$author.ID
  
  # calculate P(Aik|Seen,Co, xi) and store in A
  
  
  # remove column titled "NA"
  p_A1k.seen <- p_A1k.seen[!is.na(names(p_A1k.seen))]
  coauthor.seen.matrix = coauthor.seen.matrix[!is.na(names(coauthor.seen.matrix))]
  
  
  p_A1k.seen=as.data.frame(p_A1k.seen, stringsAsFactors = False)
  
  for (i in 1: nrow(coauthor.seen.matrix)) {
    for (j in 2: ncol(coauthor.seen.matrix)) {
      
      if(coauthor.seen.matrix[i,j] !=0)
        p_A1k.seen[i,j] <- as.numeric(coauthor.seen.matrix[i,j])/sum(as.numeric(coauthor.seen.matrix[i,-1]))  
      else p_A1k.seen[i,j] =  (1/(ncol(coauthor.seen.matrix)-1))/(1+sum(as.numeric(coauthor.seen.matrix[i,-1])))
      
      
    }
  }
  
  # calculate P(A1k|co, unseen, xi)
  
  author.coauthor.total = ncol(coauthor.matrix) + numauthor
  
  for (i in 1: numauthor)
  {
    numcoauthor[i] = sum(coauthor.matrix[i,-1]!=0)
  }
  
  p_A1k.unseen = 1/(author.coauthor.total - as.numeric(numcoauthor))
  
  
  ## Caculate P(A1k|Xi)
  
  # P(A1k|Seen,Co,Xi)
  p_A1k.seen <- as.matrix(p_A1k.seen)
  # P(Co|Xi)
  p_coauthor <- 1-p_numpapernocoauthor #26*1
  
  # P(A1k|Unseen,Co,Xi)
  #dim(p_A1k.unseen) # 26*1
  p_A1k.unseen <- as.matrix(p_A1k.unseen)
  # P(Unseen|Co,Xi)
  p_unseen.co <- 1-p_seen.co
  
  ############################################################################
  
  
  # Caculate P(A1k|Xi)
  p_A1k.X <- data.frame (matrix(rep(0,(ncol(p_A1k.seen)-1)*numauthor),nrow = numauthor))# 26*245
    p_A1k.seen <- data.frame(p_A1k.seen)
  ID <- coauthor.matrix$ author.ID
  #ID <- p_A1k.seen$author.ID
  p_A1k.X <- data.frame(ID,p_A1k.X)
  colnames(p_A1k.X) <- colnames(p_A1k.seen)
  
  
  for (i in 1:max(numauthor))
  {
    if(!(i %in% as.numeric(coauthor.unseen.matrix$author.ID)))
    {
      coauthor.unseen.matrix = rbind(coauthor.unseen.matrix, rep(1/sum(as.numeric(numcoauthor)), ncol(coauthor.unseen.matrix)))
      coauthor.unseen.matrix[nrow(coauthor.unseen.matrix), 1] = i
    }
  }
  # creating unseen coauthor probability matrix
  for(i in 2:ncol(coauthor.unseen.matrix))
  {
    coauthor.unseen.matrix[, i] = p_A1k.unseen
  }
  
  #coauthor.unseen.matrix$author.ID = coauthor.seen.matrix$author.ID

  p_A1k.X.unseen <- data.frame (matrix(rep(0.1/ncol(coauthor.unseen.matrix),(ncol(coauthor.unseen.matrix)-1)*numauthor),nrow = numauthor))
  ID <- coauthor.matrix$ author.ID
  p_A1k.X.unseen <- data.frame(ID,p_A1k.X.unseen)
  colnames(p_A1k.X.unseen) <- colnames(coauthor.unseen.matrix)
  
  for (i in 2: ncol(coauthor.unseen.matrix)) 
  {
   p_A1k.X.unseen[, i] <-   as.numeric(as.matrix(coauthor.unseen.matrix[, i])) * p_unseen.co * p_coauthor 
  }
  
  for (i in 2: ncol(p_A1k.X)) 
  {
    p_A1k.X[,i] <-  as.numeric(as.matrix(p_A1k.seen[,i]))*p_seen.co * p_coauthor #+ p_A1k.unseen * p_unseen.co * p_coauthor 
  }
  
  p_A1k.X.final = cbind(p_A1k.X.unseen, p_A1k.X[,-1])
  
  # get rid of leading and trailing white space
  ## Caculate P(A1|Xi) = P(A11|Xi)...P(A1k|Xi)...P(A1K|Xi)
  
  # the result from A1
  p_A1k.X.logged = log(p_A1k.X.final[, -1])
  
  p_A1.X.logged <- rowSums(p_A1k.X.logged)
  
  
  p_A1.X.logged <- data.frame(ID,p_A1.X.logged)
  colnames(p_A1.X.logged) <- c('ID','log(P(A1|Xi))')
  
```
  
## Step 4: Calculate the likelihood of seeing feature two, keywords in paper title.
These values are the log of conditional probabilities of author Xi writing a paper with a specific keyword in the title.

```{r}
  # extract all paper titles and put them into a list
  paper.count <- data.frame(cbind(train$author.ID, as.character(train$paper.title)))
  colnames (paper.count) = c("author.ID", "Paper.title")
  
  # clean paper title
  library(tm)
  library(tidytext)
  str(paper.count$Paper.title)
  
  corpus <- Corpus(VectorSource(paper.count$Paper.title))
  corpus <- tm_map(corpus, tolower)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, PlainTextDocument)
  #corpus <- tm_map(corpus, removeWords, stopwords('english'))
  #corpus <- tm_map(corpus, stemDocument)
  
  paper.count[,2] <- data.frame(corpus$content$content)
  
  # caculate number of words in sentence and store in paper.count
  library(stringr)
  
  word.count <- data.frame(matrix(rep(0,nrow(paper.count)),nrow = nrow(paper.count)))
  for(i in 1: nrow(paper.count)){
    word.count[i,] <- str_count(paper.count[i,2], '\\s+')+1
  }
  colnames(word.count) <-'word.count'
  paper.count <- data.frame(paper.count,word.count)
  
  # split sentence into word and store in voc.count
  List <- strsplit(as.character(paper.count$Paper.title), " ")
  voc.count <- data.frame(author.ID=rep(paper.count$author.ID, sapply(List, length)), Words=unlist(List))
  
  # generate a paper matrix
  library(reshape2)
  paper.matrix <-dcast(voc.count, author.ID~Words)
  paper.matrix[is.na(paper.matrix)]=0
  
  ## calculate P(A2k| Xi)
  # generate an empty matrix with same dim with paper.matrix
  
  p_A2k.X <- data.frame(matrix(rep(0,ncol(paper.matrix)*nrow(paper.matrix)),nrow = nrow(paper.matrix)))
  author.ID <- paper.matrix$author.ID
  p_A2k.X <- data.frame(author.ID, p_A2k.X)
  colnames(p_A2k.X) <- colnames(paper.matrix)
  
  p_A2k.X <- p_A2k.X[!is.na(names(p_A2k.X))]
  paper.matrix <- paper.matrix[!is.na(names(paper.matrix))]
  
  
  
  # lol
  for (i in 1: nrow(p_A2k.X)) {
    for (j in 2: ncol(p_A2k.X)) {
      
      if(paper.matrix[i,j] != 0)
        p_A2k.X[i,j] <- as.numeric(paper.matrix[i,j])/sum(as.numeric(paper.matrix[i,]))
      else p_A2k.X[i,j] <- (1/(ncol(paper.matrix)-1))/(1+sum(as.numeric(paper.matrix[i,])))
    }
  }
  # lol
  
  p_A2k.X.logged = log(p_A2k.X[, -1])
  
  p_A2.X.logged <- rowSums(p_A2k.X.logged)
  
  
  p_A2.X.logged <- data.frame(ID,p_A2.X.logged)
  colnames(p_A2.X.logged) <- c('ID','log(P(A2|Xi))')
```  
  
  
## Step 5: Calculate the likelihood of seeing feature two, keywords in journal title.
These values are the log of conditional probabilities of author Xi publishing in a journal with a name that includes a keyword.

  
```{r}
  # extract all paper titles and put them into a list
  paper.count <- data.frame(cbind(train$author.ID, as.character(train$journal.title)))
  colnames (paper.count) = c("author.ID", "journal.title")
  
  # clean journal title
  str(paper.count$journal.title)
  
  corpus <- Corpus(VectorSource(paper.count$journal.title))
  corpus <- tm_map(corpus, tolower)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, PlainTextDocument)
  #corpus <- tm_map(corpus, removeWords, stopwords('english'))
  #corpus <- tm_map(corpus, stemDocument)
  
  paper.count[,2] <- data.frame(corpus$content$content)
  
  # caculate number of words in sentence and store in paper.count
  library(stringr)
  
  word.count <- data.frame(matrix(rep(0,nrow(paper.count)),nrow = nrow(paper.count)))
  for(i in 1: nrow(paper.count)){
    word.count[i,] <- str_count(paper.count[i,2], '\\s+')+1
  }
  colnames(word.count) <-'word.count'
  paper.count <- data.frame(paper.count,word.count)
  
  # split sentence into word and store in voc.count
  List <- strsplit(as.character(paper.count$journal.title), " ")
  voc.count <- data.frame(author.ID=rep(paper.count$author.ID, sapply(List, length)), Words=unlist(List))
  
  # generate a paper matrix
  journal.matrix <-dcast(voc.count, author.ID~Words)
  journal.matrix[is.na(journal.matrix)]=0
  
  ## calculate P(A2k| Xi)
  # generate an empty matrix with same dim with journal.matrix
  
  p_A3k.X <- data.frame(matrix(rep(0,ncol(journal.matrix)*nrow(journal.matrix)),nrow = nrow(journal.matrix)))
  author.ID <- journal.matrix$author.ID
  p_A3k.X <- data.frame(author.ID, p_A3k.X)
  colnames(p_A3k.X) <- colnames(journal.matrix)
  
  p_A3k.X <- p_A3k.X[!is.na(names(p_A3k.X))]
  journal.matrix <- journal.matrix[!is.na(names(journal.matrix))]
  
  
  for (i in 1: nrow(p_A3k.X)) {
    for (j in 2: ncol(p_A3k.X)) {
      if(journal.matrix[i,j] != 0)
        p_A3k.X[i,j] <- as.numeric(journal.matrix[i,j])/sum(as.numeric(journal.matrix[i,]))
      else p_A3k.X[i,j] <- (1/(ncol(journal.matrix)-1))/(1+sum(as.numeric(journal.matrix[i,])))
    }
  }
  
  
  p_A3k.X.logged = log(p_A3k.X[, -1])
  
  p_A3.X.logged <- rowSums(p_A3k.X.logged)
  
  
  p_A3.X.logged <- data.frame(ID,p_A3.X.logged)
  colnames(p_A2.X.logged) <- c('ID','log(P(32|Xi))')
```  
  
  
## Step 6: Combining results into one dataframe
Here the dataframe "df" has author ID as rows, and the three features: coauthor, paper title, and journal title as columns.


```{r results = "hide"}  
  df = cbind(p_A1k.X.logged, p_A2k.X.logged, p_A3k.X.logged)
  
  trim.leading <- function (x)  sub("^\\s+", "", x)
  trim.trailing <- function (x) sub("\\s+$", "", x)
  
  colnames(df) = trim.leading(trim.trailing(colnames(df)))
  colnames(df) <- sub("\\s+", ".", colnames(df))
  colnames((df))
  
  df = cbind(df, p_xi)
  
  i = 1
  while (i < ncol(df))
  {
    if(-Inf %in% df[,i])
    {
      df[, i]=NULL
    }
    i = i+1
  }
```

## Step 7: Testing the model
We feed the features one at a time into the dataframe "df" and look up the corresponding conditional probability. We then sum the log of conditional probabilities across all the rows, resulting in a value corresponding to each author ID. Lastly, we find the maximum of the sum, and find the corresponding author ID with which.max function.

```{r}
  # this vector holds the final result of the test: rows correspond to author ID, and columns correspond to a paper
  final.result = data.frame(matrix(ncol = 0, nrow =  max(test$author.ID)))
  # actual author ID of the papers
  truth = test$author.ID
  
## Testing with feature one: coauthors
    for( i in 1:nrow(test)) 
      {# this holds the result from one paper: row corresponds to author ID,
      # columns correspond to logged probability of feature (A1, A2, A3, but so far only A1 is there)
       current.result = data.frame(matrix(ncol = 0, nrow =  max(test$author.ID)))
       # this holds one paper
       current = test[i, ]
       if(current$coauthor.names!="" & !is.na(current$coauthor.names))
       {
         coauthor.list = trim.trailing(trim.leading(unlist(strsplit(as.character(current$coauthor.names), ","))))
         coauthor.list = sub("\\s+", ".", coauthor.list)  
         # for each coauthor, get the logged probability
         for (j in 1:length(coauthor.list))
        { # 489 unique coauthors
           not_null = !(coauthor.list[j] !="")
           in_colnames = ifelse(not_null, (coauthor.list[j] %in% colnames(df)), FALSE)
           in_colnames = ifelse(is.na(in_colnames), FALSE, coauthor.list[j] %in% colnames(df))
           
           if(in_colnames)
           {
             current.result = cbind(current.result, as.data.frame(df[, coauthor.list[j]]))
           }
         }
       }
       # rind the transposed column sum of "current.result". This is the probability for A1. 
       final.result = rbind(final.result, t(rowSums(current.result)))
        
    }
  # get the prior probability in the result
  final.result = rbind(final.result, t(rowSums(current.result)), t(df$Freq))

  
## Testing with feature two: paper title     
  for( i in 1:nrow(test)) 
  {
    current.result = data.frame(matrix(ncol = 0, nrow =  max(test$author.ID)))
    current = test[i, ]
    if(current$paper.title!="" & !is.na(current$paper.title))
    {
      paper.list = trim.trailing(trim.leading(unlist(strsplit(as.character(current$paper.title), ","))))
      # for each paper keyword, get the logged probability
      for (j in 1:length(paper.list))
      { 
        not_null = !(paper.list[j] !="")
        in_colnames = ifelse(not_null, (paper.list[j] %in% colnames(df)), FALSE)
        in_colnames = ifelse(is.na(in_colnames), FALSE, paper.list[j] %in% colnames(df))
        
        if(in_colnames)
        {
          current.result = cbind(current.result, as.data.frame(df[, paper.list[j]]), df$Freq)
        }
      }
    }
    # rind the transposed column sum of "current.result". This is the probability for A2. 
    final.result = rbind(final.result, rowSums(current.result))
  }
  
  
## Testing with feature three: journal title
  
  for( i in 1:nrow(test)) 
  {current.result = data.frame(matrix(ncol = 0, nrow =  max(test$author.ID)))
   current = test[i, ]
    if(current$journal.title!="" & !is.na(current$journal.title))
    {
      journal.list = trim.trailing(trim.leading(unlist(strsplit(as.character(current$journal.title), ","))))
      # for each journal keyword, get the logged probability
      for (j in 1:length(journal.list))
      {not_null = !(journal.list[j] !="")
        in_colnames = ifelse(not_null, (journal.list[j] %in% colnames(df)), FALSE)
        in_colnames = ifelse(is.na(in_colnames), FALSE, journal.list[j] %in% colnames(df))
        if(in_colnames)
        {
          current.result = cbind(current.result, as.data.frame(df[, journal.list[j]]), df$Freq)
        }
      }
    }
    # rind the transposed column sum of "current.result". This is the probability for A3. 
    final.result = rbind(final.result, rowSums(current.result))
  }
  
  
  
## Combining the results
  answer = matrix()
  for(i in 1:nrow(test))
  {
    answer[i] = which.max(as.numeric(final.result[i, ]))
  }
  
  # this variable pits predicted value with the actual value.
  presentation = cbind(as.data.frame(answer), as.data.frame(truth))
  
 







```

# Step 8: Evaluation


```{r}

source('../lib/evaluation_measures.R')
matching_matrix_NB <- matching_matrix(test$author.ID, answer)
performance_NB <- performance_statistics(matching_matrix_NB)
compare_df <- data.frame(method=c("Naive Bayes"),
                         precision=performance_NB$precision,
                         recall=performance_NB$recall,
                         f1=performance_NB$f1,
                         accuracy=performance_NB$accuracy)
kable(compare_df,caption="Comparision of performance for Naive Bayes",digits = 2)


```



############################ Paper5: Error Driven Online Training Algorithm #####################

In this file, we illustrate our step-by-step procedure on the error driven online training algorithm on the nameset AKumar.txt (step0 - step3). We implement the algorithm on all name sets based on the step-by-step procedure described from step0-step3, and saved it in the "lib" folder. In step4, we report the evaluation to all namesets provided.

## Step 0: Load the packages, specify directories

```{r}
setwd("~/Desktop/Spr2017-proj4-team-9")
# here replace it with your own path or manually set it in RStudio
# to where this rmd file is located


if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)

#Create useable csv for each name set
source("~/Desktop/Spr2017-proj4-team-9/lib/data cleaner.R")
```

## Step 1: Load and process the data

```{r}
AKumar <- data.frame(scan("../data/nameset/AKumar.txt",
                          what = list(Coauthor = "", Paper = "", Journal = ""),
                          sep=">", quiet=TRUE),stringsAsFactors=FALSE)

# extract canonical author id befor "_"
  AKumar$AuthorID <- sub("_.*","", AKumar$Coauthor)
  # extract paper number under same author between "_" and first whitespace
  AKumar$PaperNO <- sub(".*_(\\w*)\\s.*", "\\1",  AKumar$Coauthor)
  # delete "<" in AKumar$Coauthor, you may need to further process the coauthor
  # term depending on the method you are using
  AKumar$Coauthor <- gsub("<","",sub("^.*?\\s","",  AKumar$Coauthor))
  # delete "<" in AKumar$Paper
  AKumar$Paper <- gsub("<","", AKumar$Paper)
  # add PaperID for furthur use, you may want to combine all the nameset files and 
  # then assign the unique ID for all the citations
   AKumar$PaperID <- rownames( AKumar)

```


## Step 2: Feature Design

As mentioned in the paper, we can use TF-IDF to collect all unique terms in each citation.  

```{r}
it_train <- itoken(AKumar$Paper, 
             preprocessor = tolower, 
             tokenizer = word_tokenizer,
             ids = AKumar$PaperID,
             # turn off progressbar because it won't look nice in rmd
             progressbar = FALSE)
vocab <- create_vocabulary(it_train, stopwords = c("a", "an", "the", "in", "on",
                                                   "at", "of", "above", "under"))

#vocab

vectorizer <- vocab_vectorizer(vocab)
dtm_train <- create_dtm(it_train, vectorizer)
dim(dtm_train)

tfidf <- TfIdf$new()
dtm_train_tfidf <- fit_transform(dtm_train, tfidf)

```


## Step 3: Implementing hierirchical clustering and training parameters 
In this section, our goal is to train the lambda on hierirchical clustering on our text file AKumar by the error driven online training method introduced in the paper5. We use the ranking perceptron to update the parameters.

```{r,warning=FALSE}
####Initialize Parameter lambda
lambda<-rep(1,nrow(dtm_train_tfidf))

#Add the Author's ID as the label column to the feature matrix for future use
dtm_train_tfidf<-cbind(dtm_train_tfidf,as.numeric(AKumar$AuthorID))


#Given the training set, we are able to generate the true clusters. 
#Based on the paper, we define true score S_star as the distance of the sum of clusterwise distance. We also define our own score function as the sum of distance of clusters that is clustered by hclust() function.


#Compute the true score S_star for the giving training data
element<-list()
S_star<-vector(length=length(unique(AKumar$AuthorID)))
for (i in 1:length(unique(AKumar$AuthorID))){
  element[[i]]<-dtm_train_tfidf[dtm_train_tfidf[,ncol(dtm_train_tfidf)]==i,]
  S_star[i]<-sum(dist(element[[i]]))/2
}
S_star<-mean(S_star)
T_star<-dtm_train_tfidf[,ncol(dtm_train_tfidf)]

K=14
k=1
lambda1 <- matrix(NA, nrow = nrow(AKumar), ncol = K)
S1 <- numeric(K)
acc <- numeric(K)
while (k<(K+1)){
  
#Implement Hierirchical Clustering 
h<-hclust(dist(dtm_train_tfidf*lambda))
#Check the result for the number of cluster equals to the number of unique authors in the dataset. 
h_result<-cutree(h,k=length(unique(AKumar$AuthorID)))

#Compute the our own score function S
S<-vector(length=length(unique(AKumar$AuthorID)))
element_s<-list()
for (i in 1:length(unique(AKumar$AuthorID))){
  element_s[[i]]<-dtm_train_tfidf[which(h_result==i),]
  S[i]<-sum(dist(element_s[[i]]))/2
}
S<-mean(S)



#Identify true author for each cluster generated by hclust() function, and assign it to each element of the cluster.

label<-dtm_train_tfidf[,ncol(dtm_train_tfidf)]
author.clust <- vector(length=length(unique(AKumar$AuthorID)))
for (i in 1:length(unique(AKumar$AuthorID))){
    author.clust[i]<-as.numeric(names(which.max(table(label[which(h_result==i)]))))
}

for (i in 1:unique(AKumar$AuthorID)){
    h_result[h_result==i]<-author.clust[i]
}
T_hat<-h_result

#Update lambda

for (i in 1:length(T_star)){
  if (T_hat[i]!=T_star[i]){
    lambda[i]<-lambda[i]-((S-S_star)/S) #!!!
  }
  else {
    lambda[i]<-lambda[i]
  }
}
lambda1[,k] <- lambda
S1[k] <- S
acc[k] <- mean(label == h_result)    
k=k+1
}

#plot(acc)
#lambda1[,K]
h_new<-hclust(dist(dtm_train_tfidf*lambda))
T_hat_overall<-cutree(h_new,k=unique(AKumar$AuthorID))

```


## Step 5: Evaluation on all dataset 

```{r,warning=FALSE}
source('../lib/evaluation_measures.R') 
source('../lib/data cleaner.R')

#performance statistics for AKumar
matching_matrix_hclust <- matching_matrix(AKumar$AuthorID,T_hat_overall) 
performance_hclust.AK <- performance_statistics(matching_matrix_hclust)
performance_hclust.AK

source('../lib/Y Chen.R') 
performance_hclust
source('../lib/KTanaka.R')
performance_hclust.KT
source('../lib/JSmith.R')
performance_hclust.JS
source('../lib/MMiller.R')
performance_hclust.MM
source('../lib/MBrown.R')
performance_hclust.MB
source('../lib/MJones.R')
performance_hclust.MJ
source('../lib/JLee.R')
performance_hclust.JL
source('../lib/JMartin.R')
performance_hclust.JM
source('../lib/JRobinson.R')
performance_hclust.JR
source('../lib/DJohnson.R')
performance_hclust.DJ
source('../lib/CChen.R')
performance_hclust.CC
source('../lib/AGupta.R')
performance_hclust.AG

#compute average of the all four performance statistics
Precision<-c(performance_hclust.AK$precision,performance_hclust$precision,performance_hclust.MB$precision,performance_hclust.KT$precision,performance_hclust.JS$precision,performance_hclust.MM$precision,performance_hclust.MJ$precision,performance_hclust.JL$precision,performance_hclust.JM$precision,performance_hclust.JR$precision,performance_hclust.DJ$precision,performance_hclust.CC$precision,performance_hclust.AG$precision)

Recall<-c(performance_hclust.AK$recall,performance_hclust$recall,performance_hclust.MB$recall,performance_hclust.KT$recall,performance_hclust.JS$recall,performance_hclust.MM$recall,performance_hclust.MJ$recall,performance_hclust.JL$recall,performance_hclust.JM$recall,performance_hclust.JR$recall,performance_hclust.DJ$recall,performance_hclust.CC$recall,performance_hclust.AG$recall)


F1<-c(performance_hclust.AK$f1,performance_hclust$f1,performance_hclust.MB$f1,performance_hclust.KT$f1,performance_hclust.JS$f1,performance_hclust.MM$f1,performance_hclust.MJ$f1,performance_hclust.JL$f1,performance_hclust.JM$f1,performance_hclust.JR$f1,performance_hclust.DJ$f1,performance_hclust.CC$f1,performance_hclust.AG$f1)



Accuracy<-F1<-c(performance_hclust.AK$accuracy,performance_hclust$accuracy,performance_hclust.MB$accuracy,performance_hclust.KT$accuracy,performance_hclust.JS$accuracy,performance_hclust.MM$accuracy,performance_hclust.MJ$accuracy,performance_hclust.JL$accuracy,performance_hclust.JM$accuracy,performance_hclust.JR$accuracy,performance_hclust.DJ$accuracy,performance_hclust.CC$accuracy,performance_hclust.AG$accuracy)

#Final Performance Summary combining all 14 namesets.
error.driven<-data.frame(Precision=mean(Precision),Recall=mean(Recall),F1=mean(F1),Accuracy=mean(Accuracy))
error.driven
```

#Compare the performance of two algorithms

```{r}

compare_df <- data.frame(method=c("Naive Bayes","Error Driven Algorithm"),
                         precision=c(performance_NB$precision,error.driven$Precision),
                         recall=c(performance_NB$recall,error.driven$recall),
                         f1=c(performance_NB$f1,error.driven$F1),
                         accuracy=c(performance_NB$accuracy,error.driven$Accuracy))
kable(compare_df,caption="Comparision of performance for Naive Bayes and Error Driven Online Training",digits = 2)


```