---
title: "Project 4 - Paper 5 Main Script"
author: "Xuehan Liu"
date: "04/05/2017"
output: pdf_document
---

This file is currently a template for implementing one of the suggested papers, Han, Zha, & Giles (2005). Due to the nature of the method, we only implement the method on a subset of the data, "AKumar.txt". In your project, you need to work on the whole dataset. You should follow the same structure as in this tutorial, but update it according to the papers you are assigned.

## Step 0: Load the packages, specify directories

```{r}
setwd("/Users/xuehan/Desktop/Spr2017-proj4-team-9/")
# here replace it with your own path or manually set it in RStudio
# to where this rmd file is located


if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)
```

## Step 1: Load and process the data

```{r}
AKumar <- data.frame(scan("../data/nameset/AKumar.txt",
                          what = list(Coauthor = "", Paper = "", Journal = ""),
                          sep=">", quiet=TRUE),stringsAsFactors=FALSE)
# This need to be modified for different name set

# extract canonical author id befor "_"
AKumar$AuthorID <- sub("_.*","",AKumar$Coauthor)
# extract paper number under same author between "_" and first whitespace
AKumar$PaperNO <- sub(".*_(\\w*)\\s.*", "\\1", AKumar$Coauthor)
# delete "<" in AKumar$Coauthor, you may need to further process the coauthor
# term depending on the method you are using
AKumar$Coauthor <- gsub("<","",sub("^.*?\\s","", AKumar$Coauthor))
# delete "<" in AKumar$Paper
AKumar$Paper <- gsub("<","",AKumar$Paper)
# add PaperID for furthur use, you may want to combine all the nameset files and 
# then assign the unique ID for all the citations
AKumar$PaperID <- rownames(AKumar)


```


## Step 2: Feature Design

```{r}
it_train <- itoken(AGupta$Paper, 
             preprocessor = tolower, 
             tokenizer = word_tokenizer,
             ids = AGupta$PaperID,
             # turn off progressbar because it won't look nice in rmd
             progressbar = FALSE)
vocab <- create_vocabulary(it_train, stopwords = c("a", "an", "the", "in", "on",
                                                   "at", "of", "above", "under"))

#vocab

vectorizer <- vocab_vectorizer(vocab)
dtm_train <- create_dtm(it_train, vectorizer)
dim(dtm_train)

tfidf <- TfIdf$new()
dtm_train_tfidf <- fit_transform(dtm_train, tfidf)

```

## Step 3: Implementing hierirchical clustering and training parameters 

#In this section, our goal is to train the lamda on hierirchical clustering on our text file by the error driven online training method in the paper5. We use the ranking perceptron to update the parameters.

```{r}
####Initial Parameter lambda
lambda<-rep(1,ncol(dtm_train_tfidf))

####Define Score Function  

#Based on the paper, we define our own score function S as , and define the true score function S* by the accuracy

#Score function
s<-function(){
  
}

#Ture Score Function
S_star<-function(){
  
}

while ((F(n_hat)-F(n_star))>0.0001){

#Implement Hierirchical Clustering 
h<-hclust(dist(dtm_train_tfidf*lambda))
#record clusters that generated in each step
h_result<-cutree(h,k=1:length(unique(AKumar$AuthorID)))
table(h_result)
plot(h)
 

subclust<-matrix(NA,nrow=nrow(h_result))
for (i in 1:nrow(h_result)){
   subclust[i]<-cutree(h,k=i)
}

lambda<-lambda+ifelse(T,1,0)+(F(n_hat)-F(n_star))
}





 




```


